Modular Deep Encoder-Decoders

### 2016-04-28 paper/draft.tex

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with title, author, date,
url and content in each entry. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. The
function can also give out content by key values such as title, author
and etc.

>>>>

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. Each json object 
contains the flollowing fields:
source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
\begin{itemize}
\item source: A string identifier of the newspaper from which the article was extracted.
\item url: The full URL from which the article was extracted.
\item date\_extracted: The timestamp of the date on which the article was extracted. It has the format YYYY-MM-DD hh:mm:ss. 
\item title: The title of the article. 
\item author: The author of the article.
\item content: The content of the article.
\end{itemize}
